\documentclass[12pt]{article}

\usepackage[margin=1.25in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

\doublespacing
\emergencystretch=3em

\begin{document}

\begin{center}
{\Large Spherical Splits for Decision Trees and Random Forests: A Short Note}

\vspace{1em}
Title Page and Declarations
\end{center}

\section*{Article type}

Short note.

\section*{Author information}

Mathias Valla

Chaire DIALog, Institut Louis Bachelier, Paris, France

Email: \href{mailto:mathias.valla@gmail.com}{mathias.valla@gmail.com}

Corresponding author: Mathias Valla

Postal address: Chaire DIALog, Institut Louis Bachelier, Paris, France

Telephone: to be completed in Editorial Manager.

\section*{Acknowledgments}

Work(s) conducted within the Research Chair DIALog under the aegis of the Risk
Foundation, a joint initiative by Universit\'e Paris-Dauphine PSL and CNP
Assurances.

\section*{Funding}

Research Chair DIALog under the aegis of the Risk Foundation.

\section*{Data availability}

The benchmark data are public PMLB datasets. Stored result tables and scripts
used to generate the manuscript figures are included in the accompanying code
repository.

\section*{Code availability}

The open-source repository for the spherical decision tree prototype and the
article results is available as
\href{https://github.com/MathiasValla/spherical-decision-trees}{MathiasValla/spherical-decision-trees}.
The repository includes \texttt{REPRODUCING\_RESULTS.md}, which documents how to
reproduce all results reported in the manuscript.

\section*{Competing interests}

The author declares no competing interests.

\end{document}
